Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | digital&nbsp;humanities&nbsp;educator </font>

### 2022-10-05 index.Rmd
width

<div class="container-fluid">
<div class="row">
  <div class="col-sm-7">
  <iframe src="news.html" width="100%" height="200" style="border: none;"></iframe>
  </div>
  <div class="col-sm-5">
  <a class="twitter-timeline" 
  data-show-screen-name="false" data-lang="en" 
  data-width="385px" 
  data-height="200px" 
  href="https://twitter.com/AndresKarjus?ref_src=twsrc%5Etfw"
  data-chrome="noheader nofooter">
  " "
  </a> 
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
  </div>
</div>

>>>>

<div class="container-fluid">
<div class="row">
  <div class="col-sm-7">
  <iframe src="news.html" width="100%" height="200" style="border: none;"></iframe>
  </div>
  <div class="col-sm-5">
  <a class="twitter-timeline" 
  data-show-screen-name="false" data-lang="en" 
  data-width="380px" 
  data-height="198px" 
  href="https://twitter.com/AndresKarjus?ref_src=twsrc%5Etfw"
  data-chrome="noheader nofooter">
  " "
  </a> 
<script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>
  </div>
</div>
